Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis

### 2018-01-31 paper.tex
Updated first part of Results section.

The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak static stability maximum just above the cold-point tropopause.
This lower-stratospheric stable layer had begun to erode during the initial spin-up period, with the maximum destabilitzation occurring at the innermost radii.
This decrease in static stability continued into the second day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}b) as the storm intensified to hurricane strength (Fig.~\ref{fig:vmax+pmin}).
Destabilization was particularly pronounced over the developing eye, where the time-mean cold-point tropopause height increased by up to one km compared to the previous day.
Over the developing eyewall and rainband regions, meanwhile, the tropopause height remained nearly constant.
During the third day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}c), static stability over the eye continued to decrease, and the cold-point tropopause height rose to nearly 20 km over the eye.
The tropopause sloped sharply downward outside of the 20-km radius, reaching a minimum altitude of 16.4 km only 45 km from the storm center.
This local minimum in tropopause height corresponded to the eyewall region, where upper-tropospheric static stability increased during this time period.
At larger radii, static stability began to increase in the layer immediately overlying the cold-point tropopause.
This stable layer sloped upward with radius, which corresponded to an upward-sloping tropopause radially outside of the eywall region.
Over the next 24 hours (Fig.~\ref{fig:n2-24hr-avgs}d), as the storm's maximum 10-m wind speed remained quasi-steady near 80 m s\textsuperscript{-1} (Fig.~\ref{fig:vmax+pmin}), the tropopause-layer static stability continued to increase.
%As this stable layer strengthened, its altitude rose slightly, which corresponded to a slight increase in tropopause height outside of the eyewall during this period.
%Within the upper troposphere radially outside of the eyewall, meanwhile, static stability decreased such that it was nearly neutral in a thin layer between the 120- and 150-km radii.
Within the eye, the layer between 16 and 19 km continued to destabilize, and the cold-point tropopause height increased to a level above 21.5 km.
This static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
Since most of the static stability variability

>>>>

The average $N^2$ over the first day of the simulation (Fig.~\ref{fig:n2-24hr-avgs}a) indicates the presence of a weak static stability maximum just above the cold-point tropopause.
Over the subsequent 24 hours, during which RI occurred, this static stability maximum weakened within the 20 km radius (Fig.~\ref{fig:n2-24-hr-avgs}b).
This decreasing $N^2$ corresponded to an increase in the tropopause height within the developing eye, maximizing at the storm center.
Outside of the eye, meanwhile, the tropopause height decresed over the eyewall region (25-60-km radius) and increased only slightly outside of the 60 km radius.
In this outer region, the lower-stratospheric $N^2$ maximum strengthened during RI.
These trends continued as the storm's intensity leveled off in the 48-72-hour period (Fig.~\ref{fig:n2-24hr-avgs}c).
The tropopause height increased to nearly 21 km at the storm center and sloped sharply downward to 16.3 km on the inner edge of the eyewall, near the 30 km radius.
This static stability evolution closely follows that observed in Hurricane Patricia (2015; \citeauthor{DuranMolinari2018} \citeyear{DuranMolinari2018}).
Since most of the static stability variability
